---
title: "Leonardo F. Nascimento CV"
author: Leonardo F. Nascimento
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: [ 'dd_cv.css', 'custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---
```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "beatrizmilz/resume") %>% 
  meta_social(
    title = "Leonardo F. Nascimento CV",
    description = paste(
      "CV made with the packages RMarkdown, pagedown, datadrivencv."
    ),
    url = "https://beatrizmilz.github.io/resume/index.html",
    image = "https://beatrizmilz.github.io/resume/img/share-card.png",
    image_alt = paste(
      "Leonardo F. Nascimento CV"
    ),
    og_type = "website",
    og_author = "Leonardo F. Nascimento",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@leofn3"
  )
```
<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- final academic icons -->

 
<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>

 
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1K94BsYWkAS7N9efFvbVCSGf75D6lzDbcSQugIDhQ6w4/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)


CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


<center>
![Beatriz Milz](https://avatars.githubusercontent.com/u/42153618?v=4){width=80% style='border-radius: 50%;'}
</center>



### CONTACT
<center>

<a href='https://leofn.com/' target='_blank'><i class="fa fa-home"></i></a>
 <a href='https://leofn.com/' target='_blank'><i class="fa fa-github"></i></a> <a href='mailto:leofn3@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://twitter.com/leofn3' target='_blank'><i class="fa fa-twitter"></i></a>  <a href='https://github.com/leofn' target='_blank'><i class="fa fa-github"></i></a>  <a href='https://orcid.org/0000-0003-2929-1115' target='_blank'><i class="fab fa-orcid"></i></a> <a href='http://lattes.cnpq.br/7141811368487014'  target='_blank'><i class="ai ai-lattes"></i></a>
</center>

<br>

Chemist, Psychologist and Computational Social Scientist and Programmer. I investigate disinformation, hate speech and scientific controversies in social media through NLP techniques and network analysis.

### TEACHING

<i class="fas fa-chalkboard-teacher"></i> [`tidyverse` certified trainer by RStudio](https://education.rstudio.com/trainers/people/milz+beatriz/).

<i class="fas fa-chalkboard-teacher"></i> [The Carpentries instructor](https://carpentries.org/).

<br>

### Languages

**Portuguese:** Native

**English:** Proficient

**Spanish:** Intermediate

<br>



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------
This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](http://nickstrayer.me/datadrivencv/index.html).

Code available on <i class="fa fa-github"></i>  [GitHub](https://github.com/beatrizmilz/resume). 

Last updated on `r Sys.Date()`. The most recent version of this resume is [available here](https://beatrizmilz.github.io/resume/index.pdf). 


Main
================================================================================

Beatriz Milz {#title}
--------------------------------------------------------------------------------


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching_experience')
```



Selected Oral Communications {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('oral_communications')
```


\pagebreak

::: aside

Selected activities:

### GRANTS

<i class="far fa-star"></i> [rstudio::conf()  2022](https://www.rstudio.com/conference/) - Diversity Scholarship.

<i class="far fa-star"></i> [FAPESP](https://fapesp.br/). Doctorate Scholarship - 2019-2021.

<i class="far fa-star"></i> [useR! 2019](https://user2019.r-project.org/). Diversity Scholarship - Travel and Conference.

<i class="far fa-star"></i> [LatinR 2019](https://latin-r.com/) - Travel and Conference.

<br>



### SOFTWARE

<i class="fas fa-box-open"></i> [Package {dados} - Available on CRAN](https://cienciadedatos.github.io/dados/) - Co-Author. 

<i class="fas fa-box-open"></i> [Package {mananciais}](https://beatrizmilz.github.io/mananciais/) - Author, maintainer. 

<br>

### SOFTWARE REVIEW

<i class="fas fa-box-open"></i> [R OpenSci](https://ropensci.org/): [reviews available here](https://github.com/beatrizmilz/ropensci_reviews#ropensci-reviews). 

<br>

### BOOK REVIEW

<i class="fas fa-box-open"></i> [Ecological Analysis in R](https://analises-ecologicas.com/): Book in Portuguese. Chapters 4 and 5 - Introduction to R and Tidyverse. 



<br>

### PROGRAMMING SKILLS

<i class="fab fa-r-project"></i> `R`

<i class="fa fa-area-chart" aria-hidden="true"></i>
 `tidyverse`
 
<i class="fab fa-markdown"></i> `RMarkdown / Quarto` 

<i class="fas fa-code-branch"></i> `Git`

<i class="fab fa-github"></i> `GitHub`

<i class="fab fa-markdown"></i> `Markdown`

<i class="fab fa-html5"></i> `HTML`

<i class="fab fa-css3-alt"></i> `CSS`


:::





Selected Workshops Taught {data-icon=book} 
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('workshops_taught')
```





Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```






